Oasis or Mirage? \\ Trade Network Propagation of Deforestation

### 2024-01-04 paper/main.tex
add simulation results and implications

The suppliers are located in different countries, so they have different shipping cost to the market. We assume that the cost function is a quadratic shape $c_{i} q_i ^ 2$, where $c_i$ is the sum of marginal cost to produce the goods and trade cost to supply the goods to the market. If the marginal cost is the same among three firms, then the $c_1$ is smaller than $c_2$ and $c_3$ because the supplier of country $1$ is located in the same country as the market while suppliers in country $2$ and $3$ need to transport the product with bulk log carrier. The supplier $i$'s profit function is given by 
\begin{align}
    \pi_i (q_1, q_2, q_3) = (a - \sum_{j=1}^3 q_{j}) q_{i} - c_{i} q_i ^ 2 
\end{align}

@@

Thus, we obtain 
\begin{align}
    q_1^* = \frac{4 a c_{2} c_{3} + 2 a c_{2} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 4 c_{1} + 8 c_{2} c_{3} + 8 c_{2} + 6 c_{3} + 4} \\
    q_2^* = \frac{4 a c_{1} c_{3} + 2 a c_{1} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 4 c_{1} + 8 c_{2} c_{3} + 8 c_{2} + 6 c_{3} + 4} \\
    q_3^* = \frac{4 a c_{1} c_{2} + 4 a c_{2} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 4 c_{1} + 8 c_{2} c_{3} + 8 c_{2} + 6 c_{3} + 4}
\end{align}

@@

\begin{align}
    \pi_i (q_1, q_2, 0) = (a - q_i - q_j) q_{i} - c_{i} q_i ^ 2 
\end{align}

@@

\begin{align}
    2(c_1 + 1) q_1^{**} + q_2 ^{**} + q_2 ^ {**} - a &= 0 \\
    2(c_2 + 1) q_2^{**} + q_2 ^{**} + q_1 ^ {**} - a &= 0 
\end{align}

@@

>>>>

The suppliers are located in different countries, so they have different shipping cost to the market. We assume that the cost function is a quadratic shape $c_{i} q_i ^ 2$, where $c_i$ is the sum of production cost to produce the goods and trade cost to supply the goods to the market. If the production cost is the same among three firms, then the $c_1$ is smaller than $c_2$ and $c_3$ because the supplier of country $1$ is located in the same country as the market while suppliers in country $2$ and $3$ need to transport the product with bulk log carrier. The supplier $i$'s profit function is given by 
\begin{align}
    \pi_i (q_1, q_2, q_3) = \left( a - \sum_{j=1}^3 q_{j} \right) q_{i} - c_{i} q_i ^ 2 
\end{align}

@@

Thus, we obtain 
\begin{align}
    q_1^* = \frac{4 a c_{2} c_{3} + 2 a c_{2} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4} \\
    q_2^* = \frac{4 a c_{1} c_{3} + 2 a c_{1} + 2 a c_{3} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4} \\
    q_3^* = \frac{4 a c_{1} c_{2} + 2 a c_{1} + 2 a c_{2} + a}{8 c_{1} c_{2} c_{3} + 8 c_{1} c_{2} + 8 c_{1} c_{3} + 6 c_{1} + 8 c_{2} c_{3} + 6 c_{2} + 6 c_{3} + 4}
\end{align}

@@

\begin{align}
    \pi_i (q_1, q_2, 0) = (a - q_1 - q_2) q_{i} - c_{i} q_i ^ 2 
\end{align}

@@

\begin{align}
    2(c_1 + 1) q_1^{**} + q_2 ^{**} - a &= 0 \\
    2(c_2 + 1) q_2^{**} + q_1 ^ {**} - a &= 0 
\end{align}

@@

Finally, we would like to check how assymmetric trade cost affects each firm's equilibrium strategy (while assuming that production cost is identical among suppliers). As we can infer obviously from the equilibrium strategies, $c_i > c_j > c_k$ implies $q_i^* < q_j^* < q_k^*$ before one firm exits from the market and $c_i > c_j$ implies $q_i^{**} < q_j^{**}$ after one firm exits from the market. It implies that suppliers who need to pay large shipping cost to supply the market produce relatively small quantity. Our main interest is how different trade cost affects suppliers' reaction to the other supplier's exit. The difference in equilibrium supply quantity between before and after Country $3$'s export ban is given by:

\begin{align}
    \Delta_1 &= q_1^{**} - q_1^{*} \\
    \Delta_2 &= q_2^{**} - q_2^{*}
\end{align}

Intuitively speaking, we expect that $\Delta_i > \Delta_j$ if $c_i < c_j$. Since the form of equilibrium strategies is too complicated to analytical proove this intuitive relationship, I presents results of analytical simulation which support this intuitive property. Figure \ref{fig:cournot_simulation} displays simulation results where $a = 10$ (the intercept of the inverse demand function is $10$) and $c_3 = 1$ (supplier $3$'s cost to produce and supply $q_3$ units is $1$). I calculate $\Delta_1$ and $\Delta_2$ for a total of 121 combinations of $c_1 = 0, 1, ..., 10$ and $c_2 = 0, 1, ..., 10$. Each dot in the figure shows the magnitude relationship between $\Delta_1$ and $\Delta_2$ with its shape and the difference with its color. This figure implies that $\Delta_1 > \Delta_2$ if $c_2 > c_1$, that $\Delta_1 = \Delta_2$ if $c_2 = c_1$, and that that $\Delta_1 < \Delta_2$ if $c_2 < c_1$. In addition to this simulation, I confirm that this result is not sensitive to the value of $a$ and $c_3$. These results support the property of ``$\Delta_i > \Delta_j$ if $c_i < c_j$ ''. \\

\begin{figure}[H] 
    \centering
    \caption{Impacts of Russia's Export Restriction on Its Trade Partners' Roundwood Production}
    \includegraphics*[bb=0 0 900 700, scale=0.3]{"~/OneDrive - The University of Tokyo/deforestation/fig/cournot/trade_cost_exit.png"}
    \caption*{\small{The figure shows simulation results of $\Delta_1$ and $\Delta_2$ with $a = 10$ and $c_3 = 0$ for each $c_1 = 0, 1, ..., 10$ and $c_2 = 0, 1, ..., 10$. The square corresponds to $\Delta_1 < \Delta_2$, triangle corresponds to $\Delta_1 = \Delta_2$, and square corresponds to $\Delta_1 > \Delta_2$. The color of dots shows value of $\Delta_2 - \Delta_1$.}}
    \label{fig:cournot_simulation}
\end{figure}

Moreover, this property suggests that if supply shock happens to one market, then the supplier with the smallest transportation costs will increase its production and its supply to the market to the greatest extent. In other words, the suppliers located in the same country as the market will increase their production and supply by larger extent than the foreign suppliers. For example, if China, who imported a lot of roundwood from Russia before Russia's restriction on log export, experience reduction in imports from Russia by the restriction, then China itself increase production of roundwood and supply to the home market by larger extent than the suppliers in the other countries. In the following empirical sections, we will examine how the supply shock caused by Russia and Myanmar affects the other countries' production and trade flows. The model predicts that the impacts of the supply shock is larger for Russia's (or Myanmar's) direct trade partner, whose market experience reduction in supply, than the other countries. In other words, the reaction of countries who imported roundwood from Russia (Myanmar) increases their production rapidly while the other countries increase production towards such markets by less extent.
